---
title: "Kaggle Churn"
author: "Mike Kaminski"
date: "2023-07-12"
output: html_document
---
# Setup and Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, warning = FALSE,
                      message = FALSE, dpi = 180,
                      fig.width = 10, fig.height = 5)
```

```{r}
library(tidymodels) # broom, dials, dplyr, ggplot2, parsnip, purrr, recipes, tibble, tune, workflow, yardstick
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr,tibble, stringr, forcats, lubridate
library(corrplot)
library(themis) # needed for undersampling

```

## Kaggle Link for data
# https://www.kaggle.com/competitions/playground-series-s3e17
```{r}
raw_train <- read_csv("train.csv")
raw_test <- read_csv("test.csv")
```

Rename the columns and make factors
```{r}
train <- raw_train
test <- raw_test

colnames(train) <- c('id','prod_id','type', 'air_temp', 'proc_temp', 'rpms', 'torq', 'wear','fail', 'twf','hdf','pwf','osf','rnf')
colnames(test) <- c('id','prod_id','type', 'air_temp', 'proc_temp', 'rpms', 'torq', 'wear', 'twf','hdf','pwf','osf','rnf')

train <- train %>%
  mutate_at(vars(type, twf, hdf, pwf, osf,rnf,fail), factor)

test <- test %>%
  mutate_at(vars(type, twf, hdf, pwf, osf,rnf), factor)

```

# Explore the data
```{r}
train %>% select(-id,-prod_id) %>% summary()
test %>% select(-id,-prod_id) %>% summary()

#check for NAs
train %>%
  summarize(across(everything(),
            ~sum(is.na(.x))))
test %>%
  summarize(across(everything(),
            ~sum(is.na(.x))))
```
## Correlation
```{r}
numeric_vars <- train[, sapply(train, is.numeric)] %>% select(-id)
m <- cor(numeric_vars)
corrplot(m, col = COL1('OrRd', 10),addCoef.col = 'black')
```
air_temp and proc_temp  and torq and rpms are the only variables that have a strong correlation. wear isn't correlated with anything.

Plots
```{r}

train %>%
  # sample_n(25000) %>% 
  ggplot(aes(air_temp, proc_temp, color = fail)) +
  geom_point() +
  facet_wrap(~fail)

# table(train$failure, train$twf)

```
Box Plots
```{r}
box_func <- function(col){
  plt <- train %>%
    ggplot(aes(x = {{col}}, y = type, color = fail)) +
    geom_boxplot()
  plt
}
```

```{r}
box_func(air_temp) #+ labs(title = paste0("Boxplot of air_temp by type for failures"))
box_func(proc_temp)
box_func(rpms)
box_func(torq)
box_func(wear)

```
Failures have a higher median air temp, occur at a lower rpm, and have a higher torq rate.  Proc temp and wear are more similar for failure vs not failure.

```{r}
table(train$fail, train$twf)
table(train$fail, train$hdf)
table(train$fail, train$pwf)
table(train$fail, train$osf)
table(train$fail, train$rnf)
```
Generally, the failures occur when twf, hdf, pwf, and osf are true.  An rnf generally occurs when a failure does not occur.  It's possible that these are failure codes some how - hdf could be hydraulic failure, pwf could be power failure, osf could be operating system failure.  I'm not sure what twf and rnf could be.


```{r}
a <- train %>%
  filter(fail == 1) %>%
  mutate(across(c(twf, hdf, pwf, osf, rnf), as.numeric)-1) %>%
  mutate(row_sum = rowSums(select(., twf, hdf, pwf, osf, rnf), na.rm = TRUE)) %>%
  select(9:15) %>%
  arrange(row_sum) %>%
  group_by(row_sum) %>%
  summarise(sum = n())
a  


```
Of all the failures, 507 didn't have a value in the 5 xxf variables, 1512 had 1 value in an xxf variable, 123 had 2, 6 had 3.  So a failure doesn't necessary mean that one of the 5 xxf variables will also occur, but about 75% of time at least one of these variables will also occur.

## Building some tidymodels to predict machine failure

The main packages in the `tidymodels` suite that we will use:

`rsample`: train/test or cross validation splits
`recipes`: pre-processing of data
`parsnip`: specifying the model we want to use
`workflows` : for putting the model together and constructing the workflow
`yardstick`: model evaluation metrics
`broom` : for model outputs in a clean/tidy data frame

* Setting the recipe is just specifying the model.
* Key note here is that there are a number of helper functions (e.g., `step_normalize()`, `step_impute_median()`, `step_dummy()`) that can be useful for handling data preparation. 

Since the test data doesn't have the actual values, I'll create a validation set and test/tune on that
```{r}
set.seed(525)
validation <- initial_split(train, prop = 3/4, strata = fail)
val_train <- training(validation)
val_test <- testing(validation)

# I'll eventually want to use cross validation
set.seed(636)
folds <- vfold_cv(val_train, v = 5, strata = "fail")
```


### Down Sampling
```{r}
i <- val_train$fail
j <- val_test$fail
proportions <- matrix(c(prop.table(table(i)), prop.table(table(j))), nrow = 2, ncol = 2)
rownames(proportions) <- c("0", "1")
colnames(proportions) <- c("train", "test")
proportions

```
Both data sets contain about 1.5% failures, which is good, however the data set is incredibly imbalanced, so I will try a few different ways to account for this.

### Create a recipe
The themis package contains a function that allows for down/up sampling
I'll create a recipe for the entire datas et and for the downsampled data set.
```{r}
# recipe for unsampled data set
fail_rec <-
  recipe(fail ~., data = val_train) %>%
  update_role(id, prod_id, new_role = "ID") %>%
  step_dummy(all_nominal_predictors())

# fail_rec %>% summary()

# recipe for downsampling
fail_rec_ds <- fail_rec %>%
  step_downsample(fail, under_ratio = 1)

# recipe for upsampling
fail_rec_us <- fail_rec %>%
  step_upsample(fail, under_ratio = 1)

# fail_rec_us %>% summary()
```

### Fit a model with a recipe
The recipe is used across several steps to train the model
* Process the recipe using the training set and/or downsampled training set.
** The recipe updates the role of id and prod_id so that they're excluded and converts variables to dummy variables
* The recipe is applied to the training set
* And the recipe is applied to the test set
```{r}
# logistic regression specification
glm_spec <- logistic_reg() %>%
  set_engine("glm")

# # random forest specification
# rf_spec <- rand_forest() %>%
#   set_mode("classification") %>%
#   set_engine("ranger")

```
The random forest model can learn interactions, so that could be helpful.

### Create a workflow
* This is a way to put pieces of a model together - it pairs the model and the recipe.
* different recipes need different models, so when a model and recipe are bundled, it becomes easier to train and test workflows.
```{r}
fail_wf <- 
  workflow() %>%
  add_model(glm_spec) %>%
  add_recipe(fail_rec)
```

### Prepare the recipe and train the model from the predictors
```{r}
fail_fit <-
  fail_wf %>%
  fit(data = val_train)

```

The helper function extract_fit_parsnip extracts the model from the workflow and the tidy function in broom tidies the coefficients - among other metrics
```{r}
fail_fit %>%
  extract_fit_parsnip() %>%
  tidy() %>%
  mutate(across(2:5, round, 4))
```

### Predict on the Test data
```{r}
head(predict(fail_fit, val_test),10) # this gives us zeros and ones

fail_aug <-
  augment(fail_fit, val_test) # this will give us other variables - .pred_class, ,pred_0, ,pred_1 and puts the data into a tibble

fail_aug %>%
  select(fail, .pred_class, .pred_0, .pred_1) %>%
  mutate(across(3:4, round, 4))

```

So now we evaluate
```{r}
fail_aug %>%
  roc_curve(truth = fail, .pred_0) %>%
  autoplot()

fail_aug %>%
  roc_auc(truth = fail, .pred_0)
```
That actually performed fairly well - even without downsampling.  I'll try with downsampling to see if we can improve.
Here's the recipe from before
* fail_rec_ds <- fail_rec %>% step_downsample(fail, under_ratio = 1)

The fail workflow is the same - just with a new recipe
```{r}
fail_wf_ds <- 
  workflow() %>%
  add_model(glm_spec) %>%
  add_recipe(fail_rec_ds)
```

The fit is essentially the same as well, just adding in the new workflow
```{r}
fail_fit_ds <-
  fail_wf_ds %>%
  fit(data = val_train)
```

```{r}
fail_fit_ds %>%
  extract_fit_parsnip() %>%
  tidy() %>%
  mutate(across(2:5, round, 4))
```
```{r}
head(predict(fail_fit_ds, val_test),10) # this gives us zeros and ones

fail_aug_ds <-
  augment(fail_fit_ds, val_test) # this will give us other variables - .pred_class, ,pred_0, ,pred_1 and puts the data into a tibble

fail_aug_ds %>%
  select(fail, .pred_class, .pred_0, .pred_1) %>%
  mutate(across(3:4, round, 4))
```

So now we evaluate
```{r}
fail_aug_ds %>%
  roc_curve(truth = fail, .pred_0) %>%
  autoplot()

fail_aug_ds %>%
  roc_auc(truth = fail, .pred_0)

fail_aug %>%
  roc_auc(truth = fail, .pred_0)
```
Downsampled gave a 0.93438 accuracy
Nondownsampled gave a 0.93477 accuracy

Downsampling actually hurt the accuracy.  Had I guessed success each time, my accuracy would have been 98.5%.  These models are below that value, so neither is an appropriate model

## Apply the model from the validation set to the test set and submit to Kaggle
The fail workflow is the same - just with a new recipe
```{r}
fail_wf_us <- 
  workflow() %>%
  add_model(glm_spec) %>%
  add_recipe(fail_rec_us)
```

```{r}
recipe(~., val_train) %>%
  #step_upsample(fail, over_ratio = 1) %>%
  step_downsample(fail, over_ratio = 1) %>%
  prep() %>%
  bake(new_data = NULL) %>%
  ggplot(aes(fail)) +
  geom_bar()
```


The fit is essentially the same as well, just adding in the new workflow
```{r}
fail_fit_us <-
  fail_wf_us %>%
  fit(data = val_train)
```

```{r}
fail_fit_us %>%
  extract_fit_parsnip() %>%
  tidy() %>%
  mutate(across(2:5, round, 4))
```
### End









Fit a model with a recipe
```{r}
lr_mod <- 
  logistic_reg() %>% 
  set_engine("glm")
```

create a workflow to combine4
```{r}
fail_wflow <- 
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(fail_rec)
```

```{r}
fail_fit <- 
  fail_wflow %>% 
  fit(data = train)
```

```{r}
fail_fit %>% 
  extract_fit_parsnip() %>% 
  tidy() %>%
  mutate(across(2:5, round, 4))

```

The coefficients are fairly large compared to the others when twf, hdf, pwf, and osf equal 1.  It makes me feel that this is some type of failure code.  rnf has a small negative coefficient, which may disprove that point.

folds <- vfold_cv(val_train, v = 5, strata = "fail")

Predict
```{r}
predict(fail_fit, test)

fail_aug <- augment(fail_fit, test)
fail_aug %>% 
  select()
```

```{r}
train1 <- train %>%
  mutate(bootstraps = as.factor(paste0(failure, twf,hdf,pwf,osf,rnf)))
  
```


```{r}
machine_boot <- bootstraps(train1,times = 10, strata = bootstraps)
machine_boot$splits
```

```{r}
glm_spec <- logistic_reg() %>%
  set_engine("glm")

rf_spec <- rand_forest() %>%
  set_mode("classification") %>%
  set_engine("ranger")
```

```{r}
machine_workflow <- workflow() %>%
  add_formula(failure ~ .)
  
```

```{r}
glm_rs <- machine_workflow %>%
  add_model(glm_spec) %>%
  fit_resamples(
    resamples = machine_boot,
    control = control_resamples(save_pred = TRUE, verbose = TRUE)  
  )

```

